Pre-/Post-Trikafta in CFRD

### 2022-10-04 Colleen Wood/Pre-post Trikafta/pre_post_trikafta_analysis.Rmd
Update pre_post_trikafta_analysis.Rmd

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(lmerTest)
library(nlme)
library(broom.mixed)
library(segmented)
library(performance)
library(AGD)
library(rspiro)
library(lubridate)
library(plotly)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,fig.height = 8,fig.width = 10)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
source("~/GitHub/CF/get_genotype_class_severity.R")
knitr::opts_knit$set(root.dir = home_dir)
```

@@

df = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/analysis_data.csv",na.strings = "NA")
df$X = NULL

@@

df = df %>% 
  group_by(CFF.ID) %>% fill(MRN,.direction = "downup") %>% 
  group_by(MRN) %>% fill(CFF.ID,.direction = "downup")

@@

df$Hispanic.Latinx[is.na(df$Hispanic.Latinx)] = FALSE
df$Pancreatic.Status[is.na(df$Pancreatic.Status)] = "Sufficient"
df$G.tube.in.past.12.months[is.na(df$G.tube.in.past.12.months)] = "No"

@@

date_vars = c("DOB","Start","Date")
df[,date_vars] = lapply(df[,date_vars], function(d){
  parse_date_time(d,orders = c("mdy","ymd","dmy"),quiet = T)

@@

df$DOB[which(df$DOB > lubridate::mdy("1/1/2022"))] = 

@@

# Time from start and filtering
df = df %>% group_by(CFF.ID) %>% fill(Start,.direction = "downup")
df = df %>% mutate(Time = as.numeric(difftime(Date,Start,units = "days"))) 

@@

um_a1cs = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_a1cs.csv",na.strings = "")
um_bmi = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_bmi.csv",na.strings = "")
um_demo = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_demo.csv",na.strings = "")
um_ogtt = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_ogtt.csv",na.strings = "")
um_pfts = read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_pfts.csv",na.strings = "")
um = full_join(um_a1cs,um_bmi)
um = full_join(um,um_ogtt)
um = full_join(um,um_pfts)
um = left_join(um,um_demo)
um = um %>% filter(!is.na(CFRD.Status))
um$Age = um$Age / 365.25
df = full_join(df,um)

@@

df = df %>% group_by(CFF.ID) %>% fill(DOB,Start:CFRD.Diagnosis.Date,.direction = "downup") %>%
  ungroup() %>% filter(!is.na(Time),abs(Time) <= 730,!is.na(CFF.ID),
                       (!is.na(CFRD.Diagnosis.Date) | !is.na(CFRD.Status) | site == "UW")) %>%
  select(-MRN) %>% select(CFF.ID,site,DOB,Start,everything()) %>% rename(Site = "site")
df$Sex = as.factor(df$Sex)
levels(df$Sex) = c("F","M")

@@

df$Age = pmax(as.numeric(difftime(df$Date,df$DOB,units = "days"))/365.25,df$Age,na.rm = T)

@@

df$Age_for_BMI = ifelse(df$Age > 20,20,df$Age)
df$BMIz = y2z(df$BMI,x = df$Age_for_BMI,sex = df$Sex,ref=nl4.bmi)
df$BMIz[is.infinite(df$BMIz)] = NA
df$BMI.Percentile = pnorm(df$BMIz)*100
df$Weightz = y2z(df$Weight,x = df$Age_for_BMI,sex = df$Sex,ref=nl4.wgt)
df$BMI_group = apply(df,1,function(r){
  age = as.numeric(r["Age"])
  if(!is.na(age) & age > 19){
    bmi = as.numeric(r["BMI"])
    group = cut(bmi,c(-Inf,18.5,25,30,35,40,Inf),
        labels = c("Under Weight","Normal Weight","Overweight","Obese (Class I)",
                   "Obese (Class II)","Obese (Class III+)"),right = F)
  } else if (!is.na(age) & age <= 19){
    z = as.numeric(r["BMIz"])
    perc = pnorm(z)
    group = cut(perc,c(-Inf,5,85,95,Inf),
        labels = c("Under Weight","Normal Weight","Overweight","Obese (Class I)"),right = F)
  } else {group = NA}

@@

df$BMI_group = as.factor(df$BMI_group)
df$BMI_group = ordered(df$BMI_group,c("Under Weight","Normal Weight","Overweight",
                                      "Obese (Class I)","Obese (Class II)","Obese (Class III+)"))

@@

df$Genotype1_sev = get_cf_genotype_class_severity(df$Genotypes1)
df$Genotype2_sev = get_cf_genotype_class_severity(df$Genotypes2)

@@

old <- c("Caucasian","Black","Other")
new <- c(1,2,5)
df$ppFEV = pctpred_GLI(df$Age,df$Height/100,gender = as.numeric(df$Sex),

@@

            FEV1 = df$FEV1)
df$ppFVC = pctpred_GLI(df$Age,df$Height/100,gender = as.numeric(df$Sex),

@@

            FEV1 = df$FVC)
# T1D duration
df$CFRD.Diagnosis.Date = mdy(df$CFRD.Diagnosis.Date)
df$T1D.Duration = as.numeric(difftime(df$Date,df$CFRD.Diagnosis.Date,units = "days"))/365.25

@@

df$Before_After = cut(df$Time,c(-Inf,0,Inf),labels = c("Before","After"),right = T)

@@

df = df %>% arrange(Site,CFF.ID,Date) %>% distinct()

@@

write.csv(df, file = "./Colleen Wood/Prepost Triakfta/Data_Cleaned/analysis_data_with_UM.csv",
          row.names = F,na = "")

@@

```{r}
# Most recent before/after - limit to 2 years before start
# Want the value closest to start date before start, and most recent with respect to now from start
# (i.e. the longest time after start)
most_recent = df %>% group_by(CFF.ID,Site,Before_After) %>%
  filter(Time > -2*365) %>%
  mutate(time_new = max(Time) - Time) %>%
  arrange(time_new) %>% 
  summarise(Age = first(na.omit(Age)),BMI.Percentile = first(na.omit(BMI.Percentile)),
            Weight = first(na.omit(Weight)),Sex = first(na.omit(Sex)),
            T1D.Duration = first(na.omit(T1D.Duration)),
            G.tube.in.past.12.months = first(na.omit(G.tube.in.past.12.months)),
            Pancreatic.Status = first(na.omit(Pancreatic.Status)),
            Genotype1_sev = first(na.omit(Genotype1_sev)),
            Genotype2_sev = first(na.omit(Genotype2_sev)),
            BMIz = first(na.omit(BMIz)),Weightz = first(na.omit(Weightz)),
            FEV1 = first(na.omit(FEV1)),FVC = first(na.omit(FVC)),
            HbA1c = first(na.omit(HbA1c)),.groups = "keep") %>%
  arrange(Site,CFF.ID,Before_After)
# # Check
# t = df %>% select(CFF.ID,Site,Date,Time,Before_After,BMIz,ppFEV,ppFVC) %>%
#   group_by(CFF.ID,Site,Before_After) %>%
#   arrange(Site,CFF.ID,Before_After)
# Filter those without CFRD, and those without pre AND post
keep = most_recent %>% filter(!is.na(HbA1c)) %>%
  group_by(CFF.ID) %>% summarise(n = n()) %>%
  filter(n == 2) %>% pull(CFF.ID)
cfrd = unique(df$CFF.ID[!is.na(df$CFRD.Status) | !is.na(df$CFRD.Diagnosis.Date)])
keep = unique(keep,cfrd)
most_recent = most_recent %>% filter(CFF.ID %in% keep)
```

@@

@@

```{r}
summary(tableby( ~ ppFEV + ppFVC + BMIz,data = df[!is.na(df$average_sensor),]))
```

@@

```{r}
# Piecewise model function
piecewise = function(outcome = "HbA1c",data = df,simple = F){
  # Add spline column
  data$Change = ifelse(data$Time < 0,0,1)
  data$Change = data$Change * data$Time
  # Model
  f = as.formula(paste0(outcome,"~Time + Change + (1|CFF.ID)"))
  mod = lmer(f,data = data)
  res = tidy(mod,"fixed")
  res$effect = NULL
  # Model check if necessary
  check = check_model(mod)
  # Coordinates for model plotting
  x1_start = -365
  y1_start = res$estimate[1] + res$estimate[2]*x1_start
  x1_end = 0
  y1_end = res$estimate[1] 
  x2_start = 0
  y2_start = res$estimate[1] 
  x2_end = 365
  y2_end = res$estimate[1] + (res$estimate[2]+res$estimate[3])*x2_end
  # Plot
  p = ggplot(data,aes_string(x = "Time",y = outcome,group = "CFF.ID",color = "Site")) +
    geom_point(alpha = 0.5) + geom_line(alpha = 0.2) +
    annotate("segment",x=x1_start,y=y1_start,xend=x1_end,yend=y1_end,color = "blue",size = 1) +
    annotate("segment",x=x2_start,y=y2_start,xend=x2_end,yend=y2_end,color = "blue",size = 1) +
    xlab("Days from Trikafta Start") + theme_bw()
  # Interactive plot and model results
  return(list(plot = ggplotly(p),table = res,check = check))
}
```

@@

```{r results='asis'}
a1c = piecewise(outcome = "HbA1c",data = df)
ggplotly(a1c$plot)
kable(a1c$table,digits = 3)
```

@@

```{r results='asis'}
ppFEV = piecewise(outcome = "ppFEV",data = df)
ggplotly(ppFEV$plot)
kable(ppFEV$table,digits = 3)
```

@@

```{r results='asis'}
ppFVC = piecewise(outcome = "ppFVC",data = df)
ggplotly(ppFVC$plot)
kable(ppFVC$table,digits = 3)
```

@@

```{r results='asis'}
meansg = piecewise(outcome = "average_sensor",data = df)
ggplotly(meansg$plot)
kable(meansg$table,digits = 3)
```

@@

```{r results='asis'}
minsg = piecewise(outcome = "min_sensor",data = df)
ggplotly(minsg$plot)
kable(minsg$table,digits = 3)
```

@@

```{r results='asis'}
maxsg = piecewise(outcome = "max_sensor",data = df)
ggplotly(maxsg$plot)
kable(maxsg$table,digits = 3)
```

@@

```{r results='asis'}
over120 = piecewise(outcome = "percent_time_over_120",data = df)
ggplotly(over120$plot)
kable(over120$table,digits = 3)
```

@@

```{r results='asis'}
over140 = piecewise(outcome = "percent_time_over_140",data = df)
ggplotly(over140$plot)
kable(over140$table,digits = 3)
```

@@

```{r results='asis'}
over200 = piecewise(outcome = "percent_time_over_200",data = df)
ggplotly(over200$plot)
kable(over200$table,digits = 3)
```

@@

```{r results='asis'}
numover140 = piecewise(outcome = "avg_excur_over_140_per_day",data = df)
ggplotly(numover140$plot)
kable(numover140$table,digits = 3)
```

@@

```{r results='asis'}
numover200 = piecewise(outcome = "avg_excur_over_200_per_day",data = df)
ggplotly(numover200$plot)
kable(numover200$table,digits = 3)
```

@@

```{r results='asis'}
under70 = piecewise(outcome = "percent_time_under_70",data = df)
ggplotly(under70$plot)
kable(under70$table,digits = 3)
```

@@

```{r results='asis'}
under60 = piecewise(outcome = "percent_time_under_60",data = df)
ggplotly(under60$plot)
kable(under60$table,digits = 3)
```

@@

```{r results='asis'}
auc = piecewise(outcome = "average_auc_per_day",data = df)
ggplotly(auc$plot)
kable(auc$table,digits = 3)
```

@@

```{r results='asis'}
sd = piecewise(outcome = "standard_deviation",data = df)
ggplotly(sd$plot)
kable(sd$table,digits = 3)
```

@@

```{r results='asis'}
mage = piecewise(outcome = "r_mage",data = df)
ggplotly(mage$plot)
kable(mage$table,digits = 3)
```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(readxl)
library(lmerTest)
library(nlme)
library(broom.mixed)
library(segmented)
library(performance)
library(AGD)
library(rspiro)
library(lubridate)
library(plotly)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, fig.height = 8, fig.width = 10)
if (Sys.info()["sysname"] == "Windows") {
  home_dir <- "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux") {
  home_dir <- "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin") {
  home_dir <- "/Volumes/Documents/Work/Vigers/CF"
}
source("~/GitHub/CF/get_genotype_class_severity.R")
knitr::opts_knit$set(root.dir = home_dir)
```

@@

df <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/analysis_data.csv",
  na.strings = "NA"
)
df$X <- NULL

@@

df <- df %>%
  group_by(CFF.ID) %>%
  fill(MRN, .direction = "downup") %>%
  group_by(MRN) %>%
  fill(CFF.ID, .direction = "downup")

@@

df$Hispanic.Latinx[is.na(df$Hispanic.Latinx)] <- FALSE
df$Pancreatic.Status[is.na(df$Pancreatic.Status)] <- "Sufficient"
df$G.tube.in.past.12.months[is.na(df$G.tube.in.past.12.months)] <- "No"

@@

date_vars <- c("DOB", "Start", "Date")
df[, date_vars] <- lapply(df[, date_vars], function(d) {
  parse_date_time(d, orders = c("mdy", "ymd", "dmy"), quiet = T)

@@

df$DOB[which(df$DOB > lubridate::mdy("1/1/2022"))] <-

@@

@@

df <- df %>%
  group_by(CFF.ID) %>%
  fill(Start, .direction = "downup")
df <- df %>% mutate(Time = as.numeric(difftime(Date, Start, units = "days")))
um_a1cs <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_a1cs.csv", na.strings = "")
um_bmi <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_bmi.csv", na.strings = "")
um_demo <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_demo.csv", na.strings = "")
um_race <- read_excel("./Colleen Wood/Prepost Triakfta/Data_Raw/Data from UofM/CF_race_data.xlsx")
um_race <- um_race %>%
  select(`CFF ID`, Race) %>%
  rename(CFF.ID = `CFF ID`)
um_race$Race <- factor(um_race$Race,
  levels = c(
    "Black or African American", "Some other race",
    "Two or more races", "White"
  ),
  labels = c("Black", "Other", "Other", "Caucasian")
)
um_ogtt <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_ogtt.csv", na.strings = "")
um_pfts <- read.csv("./Colleen Wood/Prepost Triakfta/Data_Cleaned/um_pfts.csv", na.strings = "")
um <- full_join(um_a1cs, um_bmi)
um <- full_join(um, um_ogtt)
um <- full_join(um, um_pfts)
um <- left_join(um, um_demo)
um <- left_join(um, um_race)
um <- um %>% filter(!is.na(CFRD.Status),abs(Time) <= 365)
um$Age <- um$Age / 365.25
df <- full_join(df, um)

@@

df <- df %>%
  group_by(CFF.ID) %>%
  fill(DOB, Start:CFRD.Diagnosis.Date, .direction = "downup") %>%
  ungroup() %>%
  filter(
    !is.na(Time), abs(Time) <= 730, !is.na(CFF.ID),
    (!is.na(CFRD.Diagnosis.Date) | !is.na(CFRD.Status) | site == "UW")
  ) %>%
  select(-MRN) %>%
  select(CFF.ID, site, DOB, Start, everything()) %>%
  rename(Site = "site")
df$Sex <- as.factor(df$Sex)
levels(df$Sex) <- c("F", "M")

@@

df$Age <- pmax(as.numeric(difftime(df$Date, df$DOB, units = "days")) / 365.25, df$Age, na.rm = T)

@@

df$Age_for_BMI <- ifelse(df$Age > 20, 20, df$Age)
df$BMIz <- y2z(df$BMI, x = df$Age_for_BMI, sex = df$Sex, ref = nl4.bmi)
df$BMIz[is.infinite(df$BMIz)] <- NA
df$BMI.Percentile <- pnorm(df$BMIz) * 100
df$Weightz <- y2z(df$Weight, x = df$Age_for_BMI, sex = df$Sex, ref = nl4.wgt)
df$BMI_group <- apply(df, 1, function(r) {
  age <- as.numeric(r["Age"])
  if (!is.na(age) & age > 19) {
    bmi <- as.numeric(r["BMI"])
    group <- cut(bmi, c(-Inf, 18.5, 25, 30, 35, 40, Inf),
      labels = c(
        "Under Weight", "Normal Weight", "Overweight", "Obese (Class I)",
        "Obese (Class II)", "Obese (Class III+)"
      ), right = F
    )
  } else if (!is.na(age) & age <= 19) {
    z <- as.numeric(r["BMIz"])
    perc <- pnorm(z)
    group <- cut(perc, c(-Inf, 5, 85, 95, Inf),
      labels = c("Under Weight", "Normal Weight", "Overweight", "Obese (Class I)"), right = F
    )
  } else {
    group <- NA
  }

@@

df$BMI_group <- as.factor(df$BMI_group)
df$BMI_group <- ordered(df$BMI_group, c(
  "Under Weight", "Normal Weight", "Overweight",
  "Obese (Class I)", "Obese (Class II)", "Obese (Class III+)"
))

@@

df$Genotype1_sev <- get_cf_genotype_class_severity(df$Genotypes1)
df$Genotype2_sev <- get_cf_genotype_class_severity(df$Genotypes2)

@@

old <- c("Caucasian", "Black", "Other")
new <- c(1, 2, 5)
df$ppFEV <- pctpred_GLI(df$Age, df$Height / 100,
  gender = as.numeric(df$Sex),

@@

  FEV1 = df$FEV1
)
df$ppFVC <- pctpred_GLI(df$Age, df$Height / 100,
  gender = as.numeric(df$Sex),

@@

  FEV1 = df$FVC
)
# uration
df$CFRD.Diagnosis.Date <- mdy(df$CFRD.Diagnosis.Date)
df$CFRD.Duration <- as.numeric(difftime(df$Date, df$CFRD.Diagnosis.Date, units = "days")) / 365.25
df$Age_group <- cut(df$Age, c(-Inf, 18, Inf), right = F, labels = c("Peds", "Adult"))

@@

df$Before_After <- cut(df$Time, c(-Inf, 0, Inf), labels = c("Before", "After"), right = T)

@@

df <- df %>%
  arrange(Site, CFF.ID, Date) %>%
  distinct()

@@

write.csv(df,
  file = "./Colleen Wood/Prepost Triakfta/Data_Cleaned/analysis_data_with_UM.csv",
  row.names = F, na = ""
)

@@

```{r}
# Most recent before/after - limit to 2 years before start
# Want the value closest to start date before start, and most recent with respect to now from start
# (i.e. the longest time after start)
pre_post <- df %>%
  group_by(CFF.ID, Before_After) %>%
  arrange(CFF.ID, Date) %>%
  summarise(
    Start = last(na.omit(Start)),
    Age = last(na.omit(Age)),
    BMI.Percentile = last(na.omit(BMI.Percentile)),
    Weight = last(na.omit(Weight)),
    CFRD.Duration = last(na.omit(CFRD.Duration)),
    Age_group = last(na.omit(Age_group)),
    Sex = last(na.omit(Sex)),
    G.tube.in.past.12.months = last(na.omit(G.tube.in.past.12.months)),
    Pancreatic.Status = last(na.omit(Pancreatic.Status)),
    Genotype1_sev = last(na.omit(Genotype1_sev)),
    Genotype2_sev = last(na.omit(Genotype2_sev)),
    BMIz = last(na.omit(BMIz)),
    ppFEV1 = last(na.omit(ppFEV)),
    ppFVC = last(na.omit(ppFVC)),
    HbA1c = last(na.omit(HbA1c)),
    Site = last(na.omit(Site)),
    .groups = "keep"
  )
# Filter those without CFRD, and those without pre AND post
keep <- df %>%
  filter(!is.na(HbA1c)) %>%
  group_by(CFF.ID) %>%
  summarise(n = n()) %>%
  filter(n == 2) %>%
  pull(CFF.ID)
cfrd <- unique(df$CFF.ID[!is.na(df$CFRD.Status) |
  df$CFRD.Status != "Impaired Glucose Tolerance (FBG < 126, 2-h PG 140-199)" |
  !is.na(df$CFRD.Diagnosis.Date)])
keep <- unique(keep, cfrd)
pre_post <- pre_post %>% filter(CFF.ID %in% keep)
two_obs <- pre_post %>%
  group_by(CFF.ID) %>%
  summarise(n = n()) %>%
  filter(n == 2) %>%
  pull(CFF.ID)
pre_post <- pre_post %>% filter(CFF.ID %in% two_obs)
# Write
write.csv(pre_post,
  file = "./Colleen Wood/Prepost Triakfta/Data_Cleaned/pre_post.csv",
  na = "", row.names = F
)
```

@@

```{r results='asis'}
t1 <- tableby(
  ~ Age + BMI.Percentile + Weight + ppFEV1 + ppFVC + CFRD.Duration + Sex + G.tube.in.past.12.months +
    Pancreatic.Status + Genotype1_sev + Genotype2_sev + Site,
  pre_post[pre_post$Before_After == "Before", ]
)
summary(t1)
```

@@

```{r}
summary(tableby(~ ppFEV + ppFVC + BMIz, data = df[!is.na(df$average_sensor), ]))
```

@@

```{r}
# Piecewise model function
piecewise <- function(outcome = "HbA1c", data = df, simple = F) {
  # Add spline column
  data$Change <- ifelse(data$Time < 0, 0, 1)
  data$Change <- data$Change * data$Time
  # Model
  f <- as.formula(paste0(outcome, "~Time + Change + (1|CFF.ID)"))
  mod <- lmer(f, data = data)
  res <- tidy(mod, "fixed")
  res$effect <- NULL
  # Model check if necessary
  check <- check_model(mod)
  # Coordinates for model plotting
  x1_start <- -365
  y1_start <- res$estimate[1] + res$estimate[2] * x1_start
  x1_end <- 0
  y1_end <- res$estimate[1]
  x2_start <- 0
  y2_start <- res$estimate[1]
  x2_end <- 365
  y2_end <- res$estimate[1] + (res$estimate[2] + res$estimate[3]) * x2_end
  # Plot
  p <- ggplot(data, aes_string(x = "Time", y = outcome, group = "CFF.ID", color = "Site")) +
    geom_point(alpha = 0.5) +
    geom_line(alpha = 0.2) +
    annotate("segment", x = x1_start, y = y1_start, xend = x1_end, yend = y1_end, color = "blue", size = 1) +
    annotate("segment", x = x2_start, y = y2_start, xend = x2_end, yend = y2_end, color = "blue", size = 1) +
    xlab("Days from Trikafta Start") +
    theme_bw()
  # Interactive plot and model results
  return(list(plot = ggplotly(p), table = res, check = check))
}
```

@@

```{r results='asis'}
a1c <- piecewise(outcome = "HbA1c", data = df)
ggplotly(a1c$plot)
kable(a1c$table, digits = 3)
```

@@

```{r results='asis'}
ppFEV <- piecewise(outcome = "ppFEV", data = df)
ggplotly(ppFEV$plot)
kable(ppFEV$table, digits = 3)
```

@@

```{r results='asis'}
ppFVC <- piecewise(outcome = "ppFVC", data = df)
ggplotly(ppFVC$plot)
kable(ppFVC$table, digits = 3)
```

@@

```{r results='asis'}
meansg <- piecewise(outcome = "average_sensor", data = df)
ggplotly(meansg$plot)
kable(meansg$table, digits = 3)
```

@@

```{r results='asis'}
minsg <- piecewise(outcome = "min_sensor", data = df)
ggplotly(minsg$plot)
kable(minsg$table, digits = 3)
```

@@

```{r results='asis'}
maxsg <- piecewise(outcome = "max_sensor", data = df)
ggplotly(maxsg$plot)
kable(maxsg$table, digits = 3)
```

@@

```{r results='asis'}
over120 <- piecewise(outcome = "percent_time_over_120", data = df)
ggplotly(over120$plot)
kable(over120$table, digits = 3)
```

@@

```{r results='asis'}
over140 <- piecewise(outcome = "percent_time_over_140", data = df)
ggplotly(over140$plot)
kable(over140$table, digits = 3)
```

@@

```{r results='asis'}
over200 <- piecewise(outcome = "percent_time_over_200", data = df)
ggplotly(over200$plot)
kable(over200$table, digits = 3)
```

@@

```{r results='asis'}
numover140 <- piecewise(outcome = "avg_excur_over_140_per_day", data = df)
ggplotly(numover140$plot)
kable(numover140$table, digits = 3)
```

@@

```{r results='asis'}
numover200 <- piecewise(outcome = "avg_excur_over_200_per_day", data = df)
ggplotly(numover200$plot)
kable(numover200$table, digits = 3)
```

@@

```{r results='asis'}
under70 <- piecewise(outcome = "percent_time_under_70", data = df)
ggplotly(under70$plot)
kable(under70$table, digits = 3)
```

@@

```{r results='asis'}
under60 <- piecewise(outcome = "percent_time_under_60", data = df)
ggplotly(under60$plot)
kable(under60$table, digits = 3)
```

@@

```{r results='asis'}
auc <- piecewise(outcome = "average_auc_per_day", data = df)
ggplotly(auc$plot)
kable(auc$table, digits = 3)
```

@@

```{r results='asis'}
sd <- piecewise(outcome = "standard_deviation", data = df)
ggplotly(sd$plot)
kable(sd$table, digits = 3)
```

@@

```{r results='asis'}
mage <- piecewise(outcome = "r_mage", data = df)
ggplotly(mage$plot)
kable(mage$table, digits = 3)
```
